\LARGE \bf \pyRobots, a toolkit for robot executive control

### 2014-08-20 paper.tex
Minor: formatting, macros...

@@

\usepackage{fixme}

@@

\title{\LARGE \bf
    {\sc pyRobots}, a executive environment for robot control
}

\author{Séverin Lemaignan, Anahita Hosseini and Pierre Dillenbourg\\
Computer-Human Interaction in Learning and Instruction \\
Ecole Polytechnique Fédérale de Lausanne (EPFL) \\
CH-1015 Lausanne, Switzerland \\
{\tt\small firstname.last@epfl.ch}
}

@@

\section{Overview of the framework}

@@

%\begin{listing}[ht]
\begin{minted}[frame=lines,
               linenos=true,
               gobble=4,
               fontsize=\scriptsize]{python}
    import time
    from robots import GenericRobot
    from robots.decorators import action, lock
    from robots.resources import Resource
    from robots.signals import ActionCancelled

@@

    @lock(WHEELS)
    @action
    def move_forward(robot):
      """ We write action in a simple imperative, 
          seemingly blocking way.
      """

@@

      try:
        while True:
          time.sleep(0.5)
      except KeyboardInterrupt:
        pass
\end{minted}
%\caption{Example from external file}
%\label{listing:3}
%\end{listing}

>>>>

  \newminted{python}{frame=lines,
                     linenos=true,
                     gobble=4,
                     fontsize=\scriptsize}

@@

\usepackage[draft]{fixme}

@@

\title{\LARGE \bf
    \pyRobots, a toolkit for robot executive control
}

\author{Séverin Lemaignan, Anahita Hosseini and Pierre Dillenbourg\\
Computer-Human Interaction in Learning and Instruction \\
École Polytechnique Fédérale de Lausanne (EPFL) \\
CH-1015 Lausanne, Switzerland \\
{\tt\small firstname.last@epfl.ch}
}

@@

\section{Concepts}

Before introducing and explaining step-by-step a complete example in the next
section, it is useful to introduce the main concepts of \pyRobots.

@@

%\begin{listing}[ht]

\begin{pythoncode}
    import time
    from robots import GenericRobot
    from robots.decorators import action, lock
    from robots.resources import Resource
    from robots.signals import ActionCancelled

@@

    @lock(WHEELS)
    @action
    def move_forward(robot):
      """ Actions are written in a simple imperative, 
          blocking style.
      """

@@

      try:
        while True:
          time.sleep(0.5)
      except KeyboardInterrupt:
        pass
\end{pythoncode}
%\caption{Example from external file}
%\label{listing:3}
%\end{listing}
